The Birth of a Galaxy: Primordial Metal Enrichment and Stellar Populations

### 2011-08-26 ApJ/ms.tex
Changing affilation to GT.

\author{John H. Wise\altaffilmark{1,2}, 
  Matthew J. Turk\altaffilmark{3},
  Michael L. Norman\altaffilmark{4},
  Tom Abel\altaffilmark{5,6,7}}

\altaffiltext{1}{Department of Astrophysical Sciences, Princeton
  University, Peyton Hall, Ivy Lane, Princeton, NJ 08544}
\altaffiltext{2}{Hubble Fellow}
\altaffiltext{3}{Department of Astronomy, Columbia University, 538
  West 120th Street, New York, NY 10027}
\altaffiltext{4}{Center for Astrophysics and Space Sciences,
  University of California at San Diego, La Jolla, CA 92093}
\altaffiltext{5}{Kavli Institute for Particle Astrophysics and
  Cosmology, Stanford University, Menlo Park, CA 94025}
\altaffiltext{6}{Zentrum f\"ur Astronomie der Universit\"at, Institut
  f\"ur Theoretische Astrophysik, Albert-Ueberle-Str. 2, 69120
  Heidelberg, Germany}
\altaffiltext{7}{Heidelberg Institut f\"ur Theoretische Studien,
  Schloss-Wolfsbrunnenweg 35, 69118 Heidelberg, Germany}

\email{jwise@astro.princeton.edu}

@@

JHW thanks Renyue Cen, Amina Helmi, Marco Spaans, and Eline Tolstoy
for enlightening discussions.  JHW is supported by NASA through Hubble
Fellowship grant \#120-6370 awarded by the Space Telescope Science
Institute, which is operated by the Association of Universities for
Research in Astronomy, Inc., for NASA, under contract NAS 5-26555.
MJT and MLN acknowledge partial support from NASA ATFP grant
NNX08AH26G.  Computational resources were provided by NASA/NCCS award
SMD-09-1439.  TA acknowledges financial support from the {\em
  Baden-W\"{u}rttemberg-Stiftung} under grant P-LS-SPII/18, the
Heidelberg Institut f\"ur Theoretische Studien. This work was
partially supported by NASA ATFP grant NNX08AH26G and NSF
AST-0807312. This research has made use of NASA’s Astrophysics Data
System Bibliographic Services.  The majority of the analysis and plots
were done with \texttt{yt} \citep{yt_full_paper}.

>>>>

\author{John H. Wise\altaffilmark{1}, 
  Matthew J. Turk\altaffilmark{2},
  Michael L. Norman\altaffilmark{3},
  Tom Abel\altaffilmark{4,5,6}}

\altaffiltext{1}{Center for Relativistic Astrophysics, School of
  Physics, Georgia Institute of Technology, 837 State Street, Atlanta,
  GA 30332}
\altaffiltext{2}{Department of Astronomy, Columbia University, 538
  West 120th Street, New York, NY 10027}
\altaffiltext{3}{Center for Astrophysics and Space Sciences,
  University of California at San Diego, La Jolla, CA 92093}
\altaffiltext{4}{Kavli Institute for Particle Astrophysics and
  Cosmology, Stanford University, Menlo Park, CA 94025}
\altaffiltext{5}{Zentrum f\"ur Astronomie der Universit\"at, Institut
  f\"ur Theoretische Astrophysik, Albert-Ueberle-Str. 2, 69120
  Heidelberg, Germany}
\altaffiltext{6}{Heidelberg Institut f\"ur Theoretische Studien,
  Schloss-Wolfsbrunnenweg 35, 69118 Heidelberg, Germany}

\email{jwise@physics.gatech.edu}

@@

JHW thanks Renyue Cen, Amina Helmi, Marco Spaans, and Eline Tolstoy
for enlightening discussions.  JHW is partially supported by NASA
through Hubble Fellowship grant \#120-6370 awarded by the Space
Telescope Science Institute, which is operated by the Association of
Universities for Research in Astronomy, Inc., for NASA, under contract
NAS 5-26555.  MJT and MLN acknowledge partial support from NASA ATFP
grant NNX08AH26G.  Computational resources were provided by NASA/NCCS
award SMD-09-1439.  TA acknowledges financial support from the {\em
  Baden-W\"{u}rttemberg-Stiftung} under grant P-LS-SPII/18, the
Heidelberg Institut f\"ur Theoretische Studien. This work was
partially supported by NASA ATFP grant NNX08AH26G and NSF
AST-0807312. This research has made use of NASA’s Astrophysics Data
System Bibliographic Services.  The majority of the analysis and plots
were done with \texttt{yt} \citep{yt_full_paper}.
